The Inner Mass-Ratio Distribution of Intermediate-Mass Stars

### 2016-02-15 paper/ms.tex
Figured out HIP 88116

We use several high spectral resolution, cross-dispersed \'echelle spectrographs for this survey. We use the CHIRON spectrograph \citep{CHIRON} on the 1.5m telescope at Cerro Tololo Inter-American Observatory for most southern targets. This spectrograph is an $R\equiv \lambda / \Delta \lambda = 80000$ spectrograph with wavelength coverage from 450 - 850 nm, and is fed by a $2.7''$ optical fiber. The data are automatically reduced with a standard CHIRON data reduction pipeline, but the pipeline leaves residuals of strong lines in adjacent orders. We therefore bias-correct, flat-field and extract the spectra with the optimum extraction technique \citep{Horne1986} using standard IRAF\footnote{IRAF is distributed by the National Optical Astronomy Observatories, which are operated by the Association of Universities for Research in Astronomy, Inc., under cooperative agreement with the National Science Foundation.} tasks, and use the wavelength calibration from the pipeline reduced spectra.

@@

As part of the follow-up effort, we used the NIRI instrument behind the Altair adaptive optics system at the Gemini North Telescope. For each star listed in Table \ref{tab:imaging_obs}, we obtained 25 images in 5 dithering positions. We used the K-continuum band centered on $2.2718\ \mu m$ and a variety of exposure times and dates (listed in Table \ref{tab:imaging_obs}). Because the targets are all extremely bright, we used the high read noise and high flux detector settings to allow for very short co-add exposure times. We reduced the data using the Gemini set of IRAF tasks, which include steps for nonlinearity correction, flat-fielding, sky subtraction, and co-addition of the dither frames.

@@

Most of the detected companions have follow-up spectra to confirm the existence of the companion. In most cases, there is a clear shift in the radial velocity of the companion, indicating that it is orbiting the target star and is not a foreground or background companion (See Figure \ref{fig:ccf}). In addition we obtained Gemini/NIRI adaptive optics imaging data for 19 of the northern companions, and were able to resolve 7 of them. We show the separation, position angle, and magnitude difference in Table \ref{tab:imaging_obs}, and display the images in Figure \ref{fig:images}.

\begin{figure}
\includegraphics[width=\columnwidth]{Imaging_Data.pdf}
\caption{Detection images for all stars in which we detect a companion in the follow-up NIRI data. 
TODO: Update imaging table. What to do with HIP 88116???}
\label{fig:images}
\end{figure}

@@

We do not use systems with more than one companion, unless the wider companion is separated by $ > 10''$ from the primary star. We mark the 48 companions we use in the mass ratio analysis with the fourth column of Table \ref{tab:companions}. Many of the companions we use in the analysis only have one detection in our data; 12/22 of these are previously known companions and so don't need follow-up to confirm. An The remaining 10 are new and unconfirmed detections; these all have very strong CCF signals and are likely to be confirmed with follow-up spectroscopy or imaging. We do not expect their inclusion to significantly alter the results. TODO: test this statement...

@@

Our mass ratio distribution appears to be in tension with the results of the VAST survey \citep{DeRosa2014}, which finds a nearly flat distribution for close companions. However, their subsample of close companions only includes 18 binaries, so it is possible that the different forms are just a result of small number statistics. To assess the degree of tension, we use the Anderson-Darling [CITE] test to find the probability that both their close companion subsample and our companions are drawn from the same parent distribution. We only use companions from this work with mean $\overline{q} > 0.15$, since the survey completeness is roughly constant in that range. To account for measurement uncertainties in the mass ratios, we choose from the mass ratio samples (see Section \ref{sec:mrd}) many times and compute the Anderson-Darling test statistic each time. Since \citet{DeRosa2014} do not quote uncertainties, we assume uncertainties of $\sigma_q = 0.05$ for all of their measurements. The result is $p = 0.02^{+0.02}_{-0.01}$, indicating that it is unlikely that both samples come from the same parent distribution.

@@

\startdata
  HIP 22833 &  4.83 &  2015-03-29 &   50x0.3 & $0.352 +/- 0.003$ & $14.1 \pm 0.7$ & $3.04 \pm 0.06$ \\
  HIP 22958 &  5.79 &  2015-10-19 &   52x0.4 & $0.445 +/- 0.003$ & $65.0 \pm 0.3$ & $2.57 \pm 0.05$ \\
  HIP 23916 &  5.98 &  2015-04-05 &   18x1.1 & \nodata & \nodata & \nodata \\
  HIP 26093 &  5.96 &  2015-03-23 &   33x0.6 & \nodata & \nodata & \nodata \\
  HIP 26126 &  5.07 &  2015-03-29 &   40x0.4 & \nodata & \nodata & \nodata \\
  HIP 29735 &  5.10 &  2015-03-22 &   83x0.2 & \nodata & \nodata & \nodata \\
  HIP 31278 &  5.46 &  2015-03-28 &   29x0.6 & \nodata & \nodata & \nodata \\
  HIP 38538 &  4.66 &  2015-10-19 &   75x0.2 & \nodata & \nodata & \nodata \\
  HIP 39847 &  4.66 &  2015-03-27 &   50x0.3 & \nodata & \nodata & \nodata \\
  HIP 75178 &  5.49 &  2015-03-24 &   29x0.6 & \nodata & \nodata & \nodata \\
  HIP 88116 &  4.47 &  2015-03-22 &   50x0.3 & $3.260 +/- 0.001$ & $210.71 \pm 0.02$ & $3.9 \pm 0.4$ \\
  HIP 91118 &  5.67 &  2015-10-16 &   43x0.4 & $0.1667 +/- 0.0007$ & $41.7 \pm 0.2$ & $1.77 \pm 0.01$ \\
 HIP 100221 &  5.70 &  2015-10-18 &   26x0.7 & $0.250 +/- 0.002$ & $346.8 \pm 0.92$ & $2.28 \pm 0.04$ \\
 HIP 100907 &  5.41 &  2015-10-16 &   43x0.4 & $0.463 +/- 0.002$ & $335.4 \pm 0.30$ & $2.91 \pm 0.04$ \\
 HIP 101909 &  $6.47^{\dagger}$ &  2015-10-16 &   39x0.5 & \nodata & \nodata & \nodata \\
 HIP 109139 &  4.40 &  2015-04-26 &   50x0.3 & \nodata & \nodata & \nodata \\
 HIP 109521 &  4.96 &  2015-04-25 &   40x0.4 & \nodata & \nodata & \nodata \\
 HIP 115115 &  4.96 &  2015-10-18 &   40x0.4 & $1.497 +/- 0.002$ & $313.14 \pm 0.08$ & $2.54 \pm 0.04$ \\
 HIP 118243 &  $5.87^{\dagger}$ &  2015-07-23 &   58x0.3 & $4.082 +/- 0.002$ & $310.23 \pm 0.03$ & $2.20 \pm 0.03$
\enddata
\tablecomments{$\dagger$: There is no K-magnitude tabulated in the Simbad Database. The value quoted here is estimated from the spectral type of the star and its V-band magnitude. TODO: I think my detection in HIP 88116 is too close to be any of the 4 companions in the image (it has a large $\Delta \mathrm{RV}$, and the expected $\Delta \mathrm{K_c}$ is about 2.7, smaller than any of the images). What should I report here?}
\label{tab:imaging_obs}
\end{deluxetable*}

>>>>

\subsection{Spectroscopic Data}
We use several high spectral resolution, cross-dispersed \'echelle spectrographs for this survey. We use the CHIRON spectrograph \citep{CHIRON} on the 1.5m telescope at Cerro Tololo Inter-American Observatory for most southern targets. This spectrograph is an $R\equiv \lambda / \Delta \lambda = 80000$ spectrograph with wavelength coverage from 450 - 850 nm, and is fed by a $2.7''$ optical fiber. The data are automatically reduced with a standard CHIRON data reduction pipeline, but the pipeline leaves residuals of strong lines in adjacent orders. We therefore bias-correct, flat-field and extract the spectra with the optimum extraction technique \citep{Horne1986} using standard IRAF\footnote{IRAF is distributed by the National Optical Astronomy Observatories, which are operated by the Association of Universities for Research in Astronomy, Inc., under cooperative agreement with the National Science Foundation.} tasks, and use the wavelength calibration from the pipeline reduced spectra.

@@

\subsection{Imaging Data}
As part of the follow-up effort, we used the NIRI instrument behind the Altair adaptive optics system at the Gemini North Telescope. For each star listed in Table \ref{tab:imaging_obs}, we obtained 25 images in 5 dithering positions. We used the K-continuum band centered on $2.2718\ \mu m$ and a variety of exposure times and dates (listed in Table \ref{tab:imaging_obs}). Because the targets are all extremely bright, we used the high read noise and high flux detector settings to allow for very short co-add exposure times. We reduced the data using the Gemini set of IRAF tasks, which include steps for nonlinearity correction, flat-fielding, sky subtraction, and co-addition of the dither frames.

We measure the flux and position of both stars by fitting a 2D Moffat function [CITE] to both stars simultaneously, constraining the shape parameters for both functions to be the same. The ratio of the amplitudes gives the magnitude difference, and the pixel locations along with the detector pixel scale gives the separation and position angle between the stars. We note that the goal of these images was confirmation and no reference tip-tilt targets were observed; the position angle uncertainty is therefore likely underestimated.

@@

Most of the detected companions have follow-up spectra to confirm the existence of the companion. In most cases, there is a clear shift in the radial velocity of the companion, indicating that it is orbiting the target star and is not a foreground or background companion (See Figure \ref{fig:ccf}). In addition we obtained Gemini/NIRI adaptive optics imaging data for 19 of the northern companions, and were able to resolve 7 of them. We show the separation, position angle, and magnitude difference in Table \ref{tab:imaging_obs}, and display the images in Figure \ref{fig:images}. One star, HIP 88116, has several nearby sources in the image. We quote the magnitude difference and separation of the brightest source in Table \ref{tab:imaging_obs}, but stress that \emph{none} of the visible sources is likely to be the companion we see in the spectroscopic data. The two epochs of spectroscopic data show a radial velocity shift of $\Delta v = 30.7 \mathrm{km\ s}^{-1}$ over the course of roughly one year; this orbital motion is much too large to allow for any of the companions visible in the image (all with separations $ > 1''$).

\begin{figure}
\includegraphics[width=\columnwidth]{Imaging_Data.pdf}
\caption{Detection images for all stars in which we detect a companion in the follow-up NIRI data. 
There are several nearby sources for HIP 88116, none of which are the source we detect in the 
spectroscopic data (see Section \ref{sec:companions}).}
\label{fig:images}
\end{figure}

@@

We do not use systems with more than one companion, unless the wider companion is separated by $ > 10''$ from the primary star. We mark the 48 companions we use in the mass ratio analysis with the fourth column of Table \ref{tab:companions}. Many of the companions we use in the analysis only have one detection in our data; 12/22 of these are previously known companions and so don't need follow-up to confirm. The remaining 10 are new and unconfirmed detections; these all have very strong CCF signals and are likely to be confirmed with follow-up spectroscopy or imaging. Their inclusion does not significantly change the results.

@@

Our mass ratio distribution appears to be in tension with the results of the VAST survey \citep{DeRosa2014}, which finds a nearly flat distribution for close companions. However, their subsample of close companions only includes 18 binaries, so it is possible that the different forms are just a result of small number statistics. To assess the degree of tension, we use the Anderson-Darling [CITE] test to find the probability that both their close companion subsample and our companions are drawn from the same parent distribution. We only use companions from this work with mean $\overline{q} > 0.15$, since the survey completeness is roughly constant in that range. To account for measurement uncertainties in the mass ratios, we choose from the mass ratio samples ($q_k^{(n)}$, see Section \ref{sec:mrd}) many times and compute the Anderson-Darling test statistic each time. Since \citet{DeRosa2014} do not quote uncertainties, we assume uncertainties of $\sigma_q = 0.05$ for all of their measurements. The result is $p = 0.02^{+0.02}_{-0.01}$, indicating that it is unlikely that both samples come from the same parent distribution.

@@

\startdata
  HIP 22833 &  4.83 &  2015-03-29 &   50x0.3 & $0.352 +/- 0.003$ & $14.1 \pm 0.7$ & $3.04 \pm 0.06$ \\
  HIP 22958 &  5.79 &  2015-10-19 &   52x0.4 & $0.445 +/- 0.003$ & $65.0 \pm 0.3$ & $2.57 \pm 0.05$ \\
  HIP 23916 &  5.98 &  2015-04-05 &   18x1.1 & \nodata & \nodata & \nodata \\
  HIP 26093 &  5.96 &  2015-03-23 &   33x0.6 & \nodata & \nodata & \nodata \\
  HIP 26126 &  5.07 &  2015-03-29 &   40x0.4 & \nodata & \nodata & \nodata \\
  HIP 29735 &  5.10 &  2015-03-22 &   83x0.2 & \nodata & \nodata & \nodata \\
  HIP 31278 &  5.46 &  2015-03-28 &   29x0.6 & \nodata & \nodata & \nodata \\
  HIP 38538 &  4.66 &  2015-10-19 &   75x0.2 & \nodata & \nodata & \nodata \\
  HIP 39847 &  4.66 &  2015-03-27 &   50x0.3 & \nodata & \nodata & \nodata \\
  HIP 75178 &  5.49 &  2015-03-24 &   29x0.6 & \nodata & \nodata & \nodata \\
  HIP 88116 &  4.47 &  2015-03-22 &   50x0.3 & $3.260 +/- 0.001$ & $210.71 \pm 0.02$ & $3.9 \pm 0.4$ \\
  HIP 91118 &  5.67 &  2015-10-16 &   43x0.4 & $0.1667 +/- 0.0007$ & $41.7 \pm 0.2$ & $1.77 \pm 0.01$ \\
 HIP 100221 &  5.70 &  2015-10-18 &   26x0.7 & $0.250 +/- 0.002$ & $346.8 \pm 0.92$ & $2.28 \pm 0.04$ \\
 HIP 100907 &  5.41 &  2015-10-16 &   43x0.4 & $0.463 +/- 0.002$ & $335.4 \pm 0.30$ & $2.91 \pm 0.04$ \\
 HIP 101909 &  $6.47^{\dagger}$ &  2015-10-16 &   39x0.5 & \nodata & \nodata & \nodata \\
 HIP 109139 &  4.40 &  2015-04-26 &   50x0.3 & \nodata & \nodata & \nodata \\
 HIP 109521 &  4.96 &  2015-04-25 &   40x0.4 & \nodata & \nodata & \nodata \\
 HIP 115115 &  4.96 &  2015-10-18 &   40x0.4 & $1.497 +/- 0.002$ & $313.14 \pm 0.08$ & $2.54 \pm 0.04$ \\
 HIP 118243 &  $5.87^{\dagger}$ &  2015-07-23 &   58x0.3 & $4.082 +/- 0.002$ & $310.23 \pm 0.03$ & $2.20 \pm 0.03$
\enddata
\tablecomments{$\dagger$: There is no K-magnitude tabulated in the Simbad Database. The value quoted here is estimated from the spectral type of the star and its V-band magnitude.}
\label{tab:imaging_obs}
\end{deluxetable*}
